% Introduction
\documentclass{article}
\usepackage{epigraph}
\usepackage{glossaries}
\usepackage{titlesec}
\titlespacing{\section}{0in}{0in}{0in}
\titlespacing{\subsection}{0in}{0in}{0in}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage[utf8]{inputenc}
\usepackage[autostyle]{csquotes}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}
\makeglossaries
\setglossarystyle{altlist}
\input{glossary.tex}
\begin{document}

\title{The Official Unoffical CMS Reference Guide for Graduate Students}
\author{Oz Amram, Lucas Corcodilos, Cristina Mantilla Suarez,\\ and other JHU graduate students}

\maketitle

\epigraph{That's one of those pieces of information in the \textit{Book of Everything You Need to Know} that nobody wrote.}{A senior graduate student}

The introductory quote (or some form of it) has been said too many times by students who know enough to fill a book but are too busy to write it. This project is meant to remedy that issue for physics at CMS. There are simply too many pieces of the collider, detectors, software, and beaurecratic structure for any one person to know everything. The success of the experiments and the analyses they perform rely on every contributor's ability to be an expert on a few things, to share their expertise, and to learn about areas of inexperience from other experts when necessary. 

One of the greatest difficulties of the final responsibility is finding the proper documentation. Even if a group within CMS does an excellent job of documenting their procedures and providing easy-to-use tools, there may not be an obvious way to look for their resources! While searching the CMS TWiki or Google is certainly an option, it typically provides search results totally unrelated to the topic of interest and it can be hard to decipher which pages are recent and which are out-of-date (not to mention all of the personal pages with wrong information!). 

This guide attempts to remedy this issue by crowd sourcing references, links, explanations, and sub-guides from the experts in one searchable document. Whether you are enitrely new and need an encyclopedia to reference or are an old hand that just needs to learn about the latest lepton scale factors, there's information for everyone. And if the information you need isn't here, go look for it and become the new resident expert by contributing what you've learned to this document! 

\section*{Sharing is caring}
Sharing knowledge is the key to this project's success so please consider contributing what you know. There's no need to write pages all at once. Just keep this document in mind after you've discovered a nuianced issue with triggers or write an email to an undergraduate describing jet reclustering. Those are excellent moments to contribute because the information is fresh in your mind and most of the work of writing it out may already be done. Simply edit the LaTeX yourself or just drop the text into an issue on GitHub and let others do it for you.

Enjoy and feel free to ask questions!

\clearpage

\input{scaling.tex}
\input{sets.tex}

% Clean page and print
\clearpage
\printglossary
\end{document}

