\section{Useful Resources (Links)}

Note that the links don't seem to work in the pdf showed by github. So download it and you should be able to access them.

\begin{itemize}
  \item \textbf{\href{https://twiki.cern.ch/twiki/bin/view/CMSPublic/WorkBook}{CMS Workbook}}:
    A decent general introduction to many of the different computing tasks. Usually only a little out of date. A good first place to look. 

  \item \textbf{\href{https://twiki.cern.ch/twiki/bin/view/CMS/WebHome}{CMS Twiki}}:
    General Twiki pages for Physics Object Groups (POG's), like Muons, Jets/MET, and Physics Analysis Groups (PAG's) like B2G, EXO, etc and other groups. 
    Usually groups keep their pages relatively up to date, but it depends on the group. This is the place to look for recommendations on common things like working points, scale factors, etc. 

  \item \textbf{\href{https://indico.cern.ch/event/639530/timetable/}{CMS Induction Course}}:
    A series of lectures for new people entering the collaboration. Gives a good overview of different areas of CMS, from detectors, to organizational structure.

  \item \textbf{\href{https://cmsweb.cern.ch/das/}{Data Aggregation System(DAS)}}:
    Look up datasets to use. See the section on using DAS.

  \item \textbf{\href{https://cms-pdmv.cern.ch/mcm/requests?page=0&shown=127}{MCM}}:
    Look up information on the production history of different datasets. Can check the configuration or parton shower settings of generator used for the MC production.
    Can search by DAS name. 

  \item \textbf{\href{https://hypernews.cern.ch/HyperNews/CMS/cindex}{Hypernews}}:
    A tool for email forums. You should subscribe to the forums related to the things you are working on. These forums are also a good place to ask for help if you have an issue or question 
    with some CMS tool and can't find help on the Twiki. People are usually helpful but it may take a few days to get a response. 

  \item \textbf{\href{https://uscms.org/uscms_at_work/physics/computing/setup/index.shtml}{LPC Tools Documentation}}:
    A good resource if you are having issues with EOS, Condor, grid certificate issues, etc. Anything related to using LPC. 

  \item \textbf{\href{https://monit-grafana.cern.ch/d/cmsTMGlobal/cms-tasks-monitoring-globalview?orgId=11}{Grafana (CRAB job monitoring)}}:
    Check how your crab jobs are doing. Select your user name in the top left box to only see your jobs. The switched to a new service as of Summer 2019 and its still a little buggy.
    Good idea to check with `crab status` if something looks weird. 

  \item \textbf{\href{http://cms.cern.ch/iCMS/analysisadmin/cadilines?awg=any&awgyear=2019}{CADI}}:
    Look up past and current analysises, contains links of most recent analysis note, paper, where they are in approval process etc. 

  \item \textbf{\href{https://github.com/cms-analysis/HiggsAnalysis-CombinedLimit/wiki}{Combine Documentation}}:
    Documentation for combine, the most common fitting tool in CMS. 





\end{itemize}


